Phonetic Tansfer analysis code

### 2022-06-01 RCode/transfer_analysis.Rmd
BLC revision final

```{r, eval=FALSE, include=FALSE}
# plot for English vowels:

# Lobanov-normalized FFs
xlim = c(2.5, -2)
ylim = c(2.3, -2)

with(df_lobanov_gender_time, plotVowels(f1, f2, vowel, group = interaction(task,context),
                               plot.tokens = F, plot.means = TRUE , pch.tokens = vowel, pch.means = interaction(task,context),
                               var.col.by = interaction(task,context), var.sty.by = gender, 
                               cex.tokens = 0.8, cex.means = 1, alpha.means = 0.5,alpha.tokens = 0.3,
                               ellipse.line = F,  ellipse.fill = F,
                               poly.line = F, poly.order = c("\\ae","\\vt"),
                               xlim = c(1,-1), ylim = c(0.5,-1), 
                               legend.kwd = "bottomright", legend.args = gender,
                               fill.opacity = 0.1, pretty = TRUE))

# raw FFs
with(df_time, plotVowels(f1, f2, vowel, group = interaction(gender, task), 
                               plot.tokens = F, plot.means = TRUE , pch.tokens = vowel, pch.means = vowel,
                               var.col.by = interaction(gender, task), var.sty.by = task, 
                               cex.tokens = 0.8, cex.means = 1, alpha.means = 0.5,alpha.tokens = 0.3,
                               ellipse.line = F,  ellipse.fill = F,
                               poly.line = F, poly.order = c("\\ae","\\vt"),
                               xlim = c(2500, 700), ylim = c(1400, 100), 
                               legend.kwd = "bottomright", legend.args = gender,
                               fill.opacity = 0.1, pretty = TRUE))

@@

## main model

>>>>

## Gender differences in IE vowels:
```{r}

# Lobanov-normalized FFs-- before gender normalization
xlim = c(3, -3)
ylim = c(4, -4)

with(df_lobanov_time, plotVowels(f1, f2, vowel, group = gender,
                               plot.tokens = F, plot.means = TRUE , pch.tokens = vowel, pch.means = vowel,
                               var.col.by = vowel, var.sty.by = gender, 
                               cex.tokens = 0.8, cex.means = 1, alpha.means = 0.5,alpha.tokens = 0.3,
                               ellipse.line = T,  ellipse.fill = T,
                               poly.line = F, poly.order = c("\\ae","\\vt"),
                               xlim = xlim, ylim = ylim, 
                               legend.kwd = "bottomright", legend.args = gender,
                               fill.opacity = 0.05, pretty = TRUE))

@@

Plots after gender normalization:

# raw FFs
with(df_lobanov_gender_time, plotVowels(f1, f2, vowel, group = gender,
                               plot.tokens = F, plot.means = TRUE , pch.tokens = vowel, pch.means = vowel,
                               var.col.by = vowel, var.sty.by = gender, 
                               cex.tokens = 0.8, cex.means = 1, alpha.means = 0.5,alpha.tokens = 0.3,
                               ellipse.line = T,  ellipse.fill = T,
                               poly.line = F, poly.order = c("\\ae","\\vt"),
                               xlim = xlim, ylim = ylim, 
                               legend.kwd = "bottomright", legend.args = gender,
                               fill.opacity = 0.05, pretty = TRUE))
